combine all centers pheno

### 2020-12-22 scripts/40_combine_all_samp_pheno.Rmd
gosh went back to the pheno table cleaning again

```{r}
I2 <- read_csv('../data/shotgun_pheno/italy_all_later.csv')

@@

# the pheno lable for the I2!
iptb <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Italy/patients/italy_essential_data_v4.xlsx', sheet = 1)
I2_pheno <- I2 %>% 
  rename(pt_id = pid) %>% 
  left_join(iptb)

I_phe <- bind_rows(
  I1 %>% 
    select(fid, pt_id = pid, infusion_date:last_followup), 
  I2_pheno %>% 
    select(fid, pt_id, infusion_date:last_followup)
) %>% 
  mutate(center = 'I')
```

>>>>

```{r}
# trying to get back the timepoint, sampleid, oligoid
# starting from the patient and their earliest sample better have pre in their raw sampleid

I2 <- read_csv('../data/shotgun_pheno/italy_all_later.csv')

isamp <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Italy/samples/opbg_sampleskey_with_oligoid_v2.xlsx', sheet = 1) %>% 
  filter(pt_id %in% I2$pid) %>% 
  filter(timepoint < 0) %>% 
  distinct(sampleid, .keep_all = T) %>% 
  full_join(I2 %>% select(pt_id = pid, fid))

@@

# the pheno lable for the I2!
iptb <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Italy/patients/italy_essential_data_v4.xlsx', sheet = 1)
I2_pheno <- isamp %>% 
  left_join(iptb)

I_phe <- bind_rows(
  I1 %>% 
    select(fid, pt_id = pid, timepoint:last_followup), 
  I2_pheno %>% 
    select(fid, pt_id, timepoint:last_followup)
) %>% 
  mutate(center = 'I')
```
